EGGs are adhesive!

### 2025-03-12 calco/main.tex
minima

\noindent
The right-hand side is a regular mono, though, and if the starting term graph is acyclic, so is also the arriving one.
Such an asymmetry between and left- and right-hand side falls in the research about left-linear rules for 
adhesive categories that has 
been pursued e.g. in~\cite{BaldanC0G24},

>>>>

\noindent
The right-hand side is a regular mono, though, and if the starting term graph is acyclic, so is also the arriving one.
Such an asymmetry between and left- and right-hand side falls in the current research about left-linear rules for 
adhesive categories, as pursued e.g. in~\cite{BaldanC0G24}.
